Figure supplements

### 2023-05-07 text/Supplements.Rmd
change figure

![**Figure 4---figure supplement 2.** **(A)** Co-expression analysis image of the NIT-GC1 (magenta) and MLD-pedal2 amide proneuropeptide gene (MLD: green). Anterior view of the larva at 2-day-old. **(B, C)** Expression analysis of the NIT-GC2 gene (magenta) using in situ HCR. Anterior (B) and posterior (C) views of the larva at 3-day-old. **(D, E)** Localisation analysis for NIT-GC1 (B) and NIT-GC2 (C) morphant using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (acTub). Anterior view of the larva at 2-day-old. **(F)** Co-localisation analysis using NIT-GC1 (magenta) and NOS (green) antibodies. Anterior view of the larva at 2-day-old.](../figures/Fig4_sup2.png){width="100%"}

>>>>

![**Figure 4---figure supplement 2.** **(A)** Co-expression analysis image of the NIT-GC1 (magenta) and MLD-pedal2 amide proneuropeptide gene (MLD: green). Anterior view of the larva at two-day-old. **(B, C)** Expression analysis of the NIT-GC2 gene (magenta) using in situ HCR. Anterior (B) and posterior (C) views of the larva at three-day-old. **(D)** Co-localisation analysis using NIT-GC1 (magenta) and NOS (green) antibodies. Anterior view of the larva at two-day-old. **(E, F)** Localisation analysis using NIT-GC1 and NIT-GC2 antibodies for NIT-GC1 (E) and NIT-GC2 (F) morphant. Green shows co-staining with acetylated α-tubulin antibody (acTub). Anterior view of the larva at two-day-old.](../figures/Fig4_sup2.png){width="100%"}

![Figure 5---figure supplement 1. Schematic diagram of the immunostaining procedure after calcium imaging.](../figures/Fig5_sup1.png){width="100%"} ![Figure 6---figure supplement 1.](../figures/Figure6_sup1.png){width="100%"}

![**Figure 6---figure supplement 2.**](../figures/Figure6_sup2.png){width="100%"}

![**Figure 6---figure supplement 3.**](../figures/Figure6_sup3.png){width="100%"}
